Prestige bias in cultural evolutionary dynamics

### 2024-06-02 ms/ms.tex
minor revision

We implement our stochastic models and approximations, perform statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.

@@

\subsection*{Dichotomous trait}
We introduce a simplified version of the above model where the trait has only two phenotypes: an optimal phenotype $\hat{A}$ and a sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability that that phenotype is transmitted and thus prestige is determined by the number of copiers that have already chosen a role-model with either phenotype.
In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous and constant ($\alpha_{i,j}=\alpha$), which entails exchangeability between role-models.
Therefore, the probability that the $i$-th copier {copies} phenotype $A$ is
\begin{equation}\label{eq:binary-model}
%G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i-1,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
G_{i,A} = \frac{\alpha \cdot (N-X) \beta(A) + (1-\alpha) \cdot K_{i-1,A}}{\alpha \cdot (N-X) \beta(A) + \alpha \cdot X + (1-\alpha)\cdot(i-1)} \;,
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i-1,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, and assuming that $\beta(\hat{A})=1$ (thus the term $\alpha X$ in the denominator).
Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
\Cref{fig:timeseries} shows some examples of model dynamics for various values of $\alpha$.

@@

Although basic, \Cref{fig:GBD} shows a good fit of the GBD approximation.
We perform more extensive validations on the Dirichlet-Multinomial approximation (see below), because that is what we will use in our analysis.

@@

\paragraph{Numerical validation.}
We next validated the DMD approximation of our model
and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DMD approximation (\Cref{cor:dirichlet}).
We used a relatively small population size, $N=100$, thus validating that the approximation is in good agreement even for small $N$, despite the assumption of large $N$ in the proof by Frigyik et al.~\citep[section 2]{dirichlet}.
First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
We then compared this observed distribution with the expected theoretical DMD (\Cref{fig:DM_validation}A).
The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
The maximum difference is 0.5 role-models, which indicates a very good fit.
In addition, we tested the likelihood of the observed data to be drawn from the DMD, against a shuffle of the parameters vector of the DMD itself (\Cref{fig:DM_validation}B). We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, strongly supporting our approximation.

Next, we examined the fixation probability and fixation time of a `successful' phenotype $\hat{A}$ (i.e., that is favored by success bias) when invading a population of phenotype $A$ and compared results from the full model and the DMD approximation.
Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
We find that the number of simulations needed to sufficiently approximate our model with the DMD approximation is roughly $1,000$ (\Cref{fig:num_sims}).
We examined the robustness of the DMD approximation to relaxing the following assumptions.
First, we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the success `bias ($A_{i,j} = A_j + e_i$).
When estimation error is applied, we sample $e_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$.
Even when the estimation error variance is $0.1$, both the fixation probability and fixation time DMD approximations are accurate~(\Cref{fig:hetro_error}). 
We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$). We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5, \epsilon)$ where $\epsilon$ is between $10^{-7}$ and $10^{-1}$. 
We found again that results of the DMD approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).

@@

\begin{figure}[h]
    \includegraphics[width=0.9\linewidth]{kimura_var.pdf}
  \caption{\textbf{Fixation probability and time in a constant environment.}
	The effect of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) on the fixation probability (\textbf{A}) and the conditional fixation time (\textbf{B}), and the effect of the success coefficient, or effective selection coefficient, $1-\beta$, on the fixation probability (\textbf{B}) and the conditional fixation time (\textbf{D}).
	Our approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
	Panel A shows a dashed line at $2(1-\beta)$, which is reached by our approximation when $\alpha=1$.
	Panel B has three lines: solid for our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals.
	Here, population size is $N=1,000$; 
	In panels A and B, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$);
	In panels C and D, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $\alpha=0.01$.
   }
  \label{fig:var_alpha}
\end{figure}

@@

\begin{figure}[H]
	\centering
    \includegraphics[width=\linewidth]{ch_env.pdf}
  \caption{\textbf{Fixation probability in a changing environment, $k<l$.}
\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis). The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange). 
\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
When success bias is large ($1-\beta > 0.1$),  
simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}). With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
(\textbf{C}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias. 
When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
Markers show average of $10,000$ simulations, error bars show 75\% (panels A and C) and 95\% (panel B) confidence intervals.
See \Cref{fig:ch_env_alpha_beta_k_large} for the scenario where $k>l$.
Here, population size is $N=1,000$;
In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=20$, and $l=80$, $\alpha=0.1$; 
In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.0198$), $\alpha=0.1$.
}
\label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error does not decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here, the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
}	
  \label{fig:influence_advantage}
\end{figure}

@@

We also analyzed the dichotomous--trait model in a periodically changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
We again derive an approximation for the fixation probability, which works well when the success coefficient $1-\beta$ is low. 
In the case of a changing environment, two key values are the number of generations $k$ and $l$  in which the invading and resident traits are favored by success bias, respectively.
When $k>l$, strong success (high $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta_k_large}),
but when $k<l$, strong prestige (low $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}A).
This is because prestige accelerates the evolutionary dynamics, which allows the invading trait to fix before the environment changes to favor the resident trait.
In all cases increasing the success coefficient $1-\beta$, which is equivalent to increasing the strength of selection, will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}B).

@@

\newpage

@@

\newpage
\section*{Supplementary Figures}
\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/

\begin{figure}[h]
    \includegraphics[width=1\linewidth]{timeseries.pdf}
  \caption{
  \textbf{Example dynamics of the dichotomous model with varying bias weight.}
  The dichotomous model is defined in \cref{eq:binary-model}. Shown are full dynamics without DM or GBD approximations.
  Here, population size, $N=1,000$; ideal phenotype value, $\hat{A}=1$; success bias value, $\beta(A)=0.99$; initial phenotype frequencies are 50\%-50\%.
  }	
  \label{fig:timeseries}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{GBD_validation.pdf}
  \caption{
  \textbf{Numerical validation of the GB approximation.}
  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. 
  Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; {ideal} phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:GBD}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=\linewidth]{DM_validation.pdf}
  \caption{
  \textbf{Numerical validation of the DM approximation.}
  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared the distribution of the number of copiers to simulations when using the DMD approximation (\Cref{cor:dirichlet}).
  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
  \textbf{(B)} The log-likelihood of the DMD for results of the simulations (red vertical line) is much higher {than} the log-likelihood of permutations of simulations (blue histogram).
  Here, population size, $N=100$; number of simulations, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
  No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
  \label{fig:DM_validation}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=\linewidth]{num_sims.pdf}
  \caption{
  \textbf{DMD approximation precision as function of number of simulations.}
  Our DMD approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
  Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
  Markers are averages across simulations, error bars are 95\% confidence intervals.
  Here, population size, $N=1000$; success-bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success-bias value, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{full_vs_dm_mutation.pdf}
  \caption{
  \textbf{Robustness of DMD approximations to success estimation error.}
  Both the DMD approximation (orange) and our approximation (black) agree with the stochastic simulations (blue), even with a high estimation error.
  Markers are averages across simulations, error bars are 95\% confidence intervals.
  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,\eta^2)$ where $\eta^2$ in on the x-axis.
  }	
  \label{fig:hetro_error}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{full_vs_dm_changing_alpha.pdf}
   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   Fixation probability does not seem to be affected by variation in success bias weight between role-models.
    Thus, both the DM approximation (orange) and Kimura's equation (black line) have a good fit to results of stochastic simulations (blue).
   Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
  Here, population size, $N=1000$; 
  success bias weight is normally distributed, $\alpha_j \sim N(0.5,\epsilon^2)$ where $10^{-7}\le \epsilon^2 \le 10^{-1}$; 
  phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
\end{figure}

\begin{figure}
	\centering
    \includegraphics[width=\linewidth]{ch_env_k_large.pdf}
  \caption{\textbf{Fixation probability in a changing environment, $k>l$.}
\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis). The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange). 
\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
When success bias is large ($1-\beta > 0.1$),  
simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}). With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
Markers show average of $10,000$ simulations, error bars show 75\% (panel A) and 95\% (panel B) confidence intervals.
Here, population size is $N=1,000$;
In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=80$, and $l=20$;
In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=80$, and $l=20$, $\alpha=0.1$; 
}
\label{fig:ch_env_alpha_beta_k_large}
\end{figure}

>>>>

We implement our stochastic models and approximations, perform statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
Source code is available on GitHub (\href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}) and deposited on Zenodo (doi:10.5281/zenodo.11424199).

@@

\subsection*{Dichotomous trait}
We introduce a simplified version of the above model where the trait has only two phenotypes: an optimal phenotype $\hat{A}$ and a sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability that that phenotype is transmitted and thus prestige is determined by the number of copiers that have already chosen a role-model with either phenotype.
In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous and constant ($\alpha_{i,j}=\alpha$), which entails exchangeability between role-models.
Therefore, the probability that the $i$-th copier {copies} phenotype $A$ is
\begin{equation}\label{eq:binary-model}
%G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i-1,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
G_{i,A} = \frac{\alpha \cdot (N-X) \beta(A) + (1-\alpha) \cdot K_{i-1,A}}{\alpha \cdot (N-X) \beta(A) + \alpha \cdot X + (1-\alpha)\cdot(i-1)} \;,
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i-1,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, and assuming that $\beta(\hat{A})=1$ (thus the term $\alpha X$ in the denominator).
Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
Figure S1 shows some examples of model dynamics for various values of $\alpha$.

@@

Although basic, Figure S2 shows a good fit of the GBD approximation.
We perform more extensive validations on the Dirichlet-Multinomial approximation (see below), because that is what we will use in our analysis.

@@

\paragraph{Numerical validation.}
We next validated the DMD approximation of our model
and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DMD approximation (\Cref{cor:dirichlet}).
We used a relatively small population size, $N=100$, thus validating that the approximation is in good agreement even for small $N$, despite the assumption of large $N$ in the proof by Frigyik et al.~\citep[section 2]{dirichlet}.
First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
We then compared this observed distribution with the expected theoretical DMD (Figure S3A).
The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
The maximum difference is 0.5 role-models, which indicates a very good fit.
In addition, we tested the likelihood of the observed data to be drawn from the DMD, against a shuffle of the parameters vector of the DMD itself (Figure S3B). We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, strongly supporting our approximation.

Next, we examined the fixation probability and fixation time of a `successful' phenotype $\hat{A}$ (i.e., that is favored by success bias) when invading a population of phenotype $A$ and compared results from the full model and the DMD approximation.
Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
We find that the number of simulations needed to sufficiently approximate our model with the DMD approximation is roughly $1,000$ (Figure S4).
We examined the robustness of the DMD approximation to relaxing the following assumptions.
First, we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the success `bias ($A_{i,j} = A_j + e_i$).
When estimation error is applied, we sample $e_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$.
Even when the estimation error variance is $0.1$, both the fixation probability and fixation time DMD approximations are accurate~(Figure S5). 
We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$). We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5, \epsilon)$ where $\epsilon$ is between $10^{-7}$ and $10^{-1}$. 
We found again that results of the DMD approximation are similar to those from stochastic simulations of the full model~(Figure S6).

@@

\begin{figure}[h]
    \includegraphics[width=0.9\linewidth]{../figures/kimura_var.pdf}
  \caption{\textbf{Fixation probability and time in a constant environment.}
	The effect of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) on the fixation probability (\textbf{A}) and the conditional fixation time (\textbf{B}), and the effect of the success coefficient, or effective selection coefficient, $1-\beta$, on the fixation probability (\textbf{B}) and the conditional fixation time (\textbf{D}).
	Our approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
	Panel A shows a dashed line at $2(1-\beta)$, which is reached by our approximation when $\alpha=1$.
	Panel B has three lines: solid for our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals.
	Here, population size is $N=1,000$; 
	In panels A and B, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$);
	In panels C and D, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $\alpha=0.01$.
   }
  \label{fig:var_alpha}
\end{figure}

@@

\begin{figure}[H]
	\centering
    \includegraphics[width=\linewidth]{../figures/ch_env.pdf}
  \caption{\textbf{Fixation probability in a changing environment, $k<l$.}
\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis). The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange). 
\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
When success bias is large ($1-\beta > 0.1$),  
simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}). With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
(\textbf{C}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias. 
When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
Markers show average of $10,000$ simulations, error bars show 75\% (panels A and C) and 95\% (panel B) confidence intervals.
See Figure S7 for the scenario where $k>l$.
Here, population size is $N=1,000$;
In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=20$, and $l=80$, $\alpha=0.1$; 
In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.0198$), $\alpha=0.1$.
}
\label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error does not decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here, the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
}	
  \label{fig:influence_advantage}
\end{figure}

@@

We also analyzed the dichotomous--trait model in a periodically changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
We again derive an approximation for the fixation probability, which works well when the success coefficient $1-\beta$ is low. 
In the case of a changing environment, two key values are the number of generations $k$ and $l$  in which the invading and resident traits are favored by success bias, respectively.
When $k>l$, strong success (high $\alpha$) will increase the fixation probability (Figure S7),
but when $k<l$, strong prestige (low $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}A).
This is because prestige accelerates the evolutionary dynamics, which allows the invading trait to fix before the environment changes to favor the resident trait.
In all cases increasing the success coefficient $1-\beta$, which is equivalent to increasing the strength of selection, will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}B).

@@

@@
